---
title: "2019-02-12_Harris_27"
author: "Nicolas May"
date: "2/20/2019"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# BUILD DATASET


## Load Requirements

### Load Packages

```{r load_packages}
library(dplyr)
library(stringr)
```

### Load Useful Globals / Functions

```{r load_globals_functions}
source("~/Desktop/config.R")
source("~/Desktop/helpers.R")

GET_API_DATA <- TRUE
```


## Get Data

### Define Data Fields/Forms

#### UDS 3

```{r}
# Header form
fields_u3_hd_vct <-
  c(
    "ptid"
    , "form_date"
  )
# A1 form
fields_u3_a1_vct <-
  c(
    "livsitua"
    # , "zip"
  ) %>% 
  c(., paste0("fu_", .), paste0("tele_", .))
# B5 form
fields_u3_b5_vct <-
  c(
    "agit"
    , "depd"
  ) %>% 
  c(., paste0("fu_", .), paste0("tele_", .))
# D1 form
fields_u3_d1_vct <-
  c(
    "normcog"
    , "demented"
  ) %>% 
  c(., paste0("fu_", .), paste0("tele_", .))

# Collapse `fields_u3_*_vct`s
fields_u3_vct <-
  c(
    fields_u3_hd_vct
    , fields_u3_a1_vct
    , fields_u3_b5_vct
    , fields_u3_d1_vct
  )
fields_u3 <- fields_u3_vct %>% paste(collapse = ",")
```

#### MiNDSet Registry

```{r}
fields_ms_hd_vct <-
  c(
    "subject_id"
    , "exam_date"
    , "zip_code"
  )

# Collapse `fields_ms_*_vct`s
fields_ms_vct <-
  c(
    fields_ms_hd_vct
  ) 
fields_ms <- fields_ms_vct %>% paste(collapse = ",")


# ZIP code vectors
# sources: 
# 1. https://zipcode.org/city/MI/DETROIT
# 2. https://zipcode.org/city/MI/ANNARBOR

# Detroit ZIP codes
zips_det <-
  c(
    "48201"
    , "48202"
    , "48206"
    , "48207"
    , "48208"
    , "48209"
    , "48213"
    , "48214"
    , "48215"
    , "48217"
    , "48219"
    , "48222"
    , "48223"
    , "48224"
    , "48204"
    , "48205"
    , "48210"
    , "48211"
    , "48216"
    , "48221"
    , "48226"
    , "48227"
    , "48228"
    , "48231"
    , "48238"
    , "48243"
    , "48244"
    , "48255"
    , "48265"
    , "48266"
    , "48269"
    , "48272"
    , "48275"
    , "48277"
    , "48232"
    , "48233"
    , "48234"
    , "48235"
    , "48242"
    , "48260"
    , "48264"
    , "48267"
    , "48268"
    , "48278"
    , "48279"
    , "48288"
  )

# Ann Arbor ZIP codes
zips_ann <-
  c(
    "48103"
    , "48104"
    , "48105"
    , "48109"
    , "48113"
    , "48106"
    , "48107"
    , "48108"
  )
```

### Retrieve Data via REDCAP API

#### UDS 3

```{r}
json_u3 <- rc_api_get(uri    = REDCAP_API_URI,
                      token  = REDCAP_API_TOKEN_UDS3n,
                      fields = fields_u3,
                      raw    = FALSE)
df_u3 <- jsonlite::fromJSON(json_u3) %>% na_if("")
```

#### MiNDSet Registry

```{r}
json_ms <- rc_api_get(uri    = REDCAP_API_URI,
                      token  = REDCAP_API_TOKEN_MINDSET,
                      fields = fields_ms,
                      raw    = FALSE)
df_ms <- jsonlite::fromJSON(json_ms) %>% na_if("")
```


## Process Data

### Clean Data

#### UDS 3

```{r}
df_u3_cln <- df_u3 %>% 
  # clean out records missing `form_date`s
  filter(!is.na(form_date)) %>% 
  # clean out DDE records
  filter(str_detect(ptid, pattern = "^UM\\d{8}$")) %>% 
  # remove useless `redcap_event_name` field
  select(-redcap_event_name)
```

#### MiNDSet Registry

```{r}
df_ms_cln <- df_ms %>% 
  # clean out missing `exam_date`s
  filter(!is.na(exam_date)) %>% 
  # clean out non UMMAP IDs
  filter(str_detect(subject_id, pattern = "^UM\\d{8}$")) %>% 
  # remove useless `redcap_event_name` field
  select(-redcap_event_name)
```


### Mutate Data

#### UDS 3

```{r}
df_u3_cln_mut <- df_u3_cln %>% 
  # coalesce IVP / FVP / TVP fields
  coalesce_ift_cols() %>% 
  # retype fields appropriately
  mutate(form_date = as.Date(form_date)) %>% 
  # clean up labelled data values
  mutate(normcog  = str_extract(normcog, "(No|Yes)"),
         demented = str_extract(demented, "(No|Yes)"),
         agit     = str_extract(agit, "(No|Yes)"),
         depd     = str_extract(depd, "(No|Yes)")) %>% 
  # if `normcog` is yes, `demented` is no
  mutate(demented = case_when(
    is.na(demented) & normcog == "Yes" ~ "No",
    TRUE ~ demented
  ))
```

#### MiNDSet Registry

```{r}
df_ms_cln_mut <- df_ms_cln %>% 
  # retype fields appropriately
  mutate(exam_date = as.Date(exam_date)) %>% 
  # get just 5-digit ZIP codes
  mutate(zip_code = str_sub(zip_code, 1, 5)) 
```

### Join Data

#### Left Outer Join: UDS 3 + MiNDSet Registry

```{r}
df_u3_ms <-
  FuzzyDateJoin::outer_left(
    x = df_u3_cln_mut,        y = df_ms_cln_mut,
    x_id_col = "ptid",        y_id_col = "subject_id",
    x_date_col = "form_date", y_date_col = "exam_date",
    x_intvl_less = 365L, x_intvl_more = 365L,
    keep_y_id = FALSE
  )
```

### Filter Joined Data

```{r}
df_u3_ms_flt <- df_u3_ms %>% 
  # keep only Detroit and Ann Arbor ZIP codes
  filter(zip_code %in% c(zips_det, zips_ann)) %>% 
  # get only latest visit
  get_visit_n(id_field = ptid, date_field = form_date, n = Inf)
```


## Write Data

### Write as CSV

```{r}
readr::write_csv(df_u3_ms_flt, "df_u3_ms_flt.csv", na = "")
```


## Summarize Data

### Dementia x Agitation (`demented` x `agit`)

```{r}
(demented_agit_summ <- df_u3_ms_flt %>% 
   group_by(demented, agit) %>% 
   tally() %>% 
   filter(!is.na(demented), !is.na(agit)) %>% 
   arrange(demented, agit) %>% 
   tidyr::spread(key = agit, value = n, sep = "_"))

readr::write_csv(demented_agit_summ, "demented_agit_summ.csv", na = "")
```

```{r}
(demented_depd_summ <- df_u3_ms_flt %>% 
  group_by(demented, depd) %>% 
  tally() %>% 
  filter(!is.na(demented), !is.na(depd)) %>%
  arrange(demented, depd) %>% 
  tidyr::spread(key = depd, value = n, sep = "_"))

readr::write_csv(demented_depd_summ, "demented_depd_summ.csv", na = "")
```

```{r}
(demented_livsitua_summ <- df_u3_ms_flt %>% 
  group_by(demented, livsitua) %>% 
  tally() %>% 
  filter(!is.na(demented), !is.na(livsitua)) %>% 
  arrange(demented, livsitua) %>% 
  tidyr::spread(key = livsitua, value = n, sep = "_"))

readr::write_csv(demented_livsitua_summ, "demented_livsitua_summ.csv", na = "")
```


# BUILD DATA DICTIONARIES


## Get Data Dictionaries

### Define Data Fields

These are already defined: `fields_u3_vct` for UDS 3 and `fields_ms_vct` for MiNDSet Registry.

### Get Data Dictionaries via REDCap API

#### UDS 3

```{r}
json_dd_u3 <- RCurl::postForm(
  uri          = REDCAP_API_URI,
  token        = REDCAP_API_TOKEN_UDS3n,
  content      = "metadata",
  format       = "json",
  returnFormat = "json"
)

df_dd_u3 <- jsonlite::fromJSON(json_dd_u3)
```

#### MiNDSet Registry

```{r}
json_dd_ms <- RCurl::postForm(
  uri          = REDCAP_API_URI,
  token        = REDCAP_API_TOKEN_MINDSET,
  content      = "metadata",
  format       = "json",
  returnFormat = "json"
)

df_dd_ms <- jsonlite::fromJSON(json_dd_ms)
```

## Filter Data Dictionaries

#### UDS 3

```{r}
df_dd_u3_flt <- df_dd_u3 %>% 
  filter(field_name %in% fields_u3_vct)
```

#### MiNDSet Registry

```{r}
df_dd_ms_flt <- df_dd_ms %>% 
  filter(field_name %in% fields_ms_vct)
```


## Write Data Dictionaries

#### UDS 3

```{r}
readr::write_csv(df_dd_u3_flt, "DataDictionary_UDS3.csv", na = "")
```

#### MiNDSet Registry

```{r}
readr::write_csv(df_dd_ms_flt, "DataDictionary_MiNDSetRegistry.csv", na = "")
```

```{r extra_space, echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
